Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
Add an other commet

>>>>

\begin{quote}
    @kazu: I think all behavior is user visible, in the way that the user can
    observe it when he uses the function.  Otherwise we would not be interested
    in that behavior at all.  What do you think about using \emph{Behavior as
    user documentation} and \emph{Behavior as code documentation} instead of
    visible/internal behavior?  Or can we come up with something else?
\end{quote}
